Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-05-01 draft/ms_v5.tex
Update the PSF mag and color tables
Update figures for PSF photometry

    In Fig \ref{fig:psf_color}, we evaluate the precision and accuracy of the 
    \forced{} $(g-i)$ and $(i-y)$ PSF colors by comparing the differences between input 
    and output colors ($\Delta \mathrm{Color}$) with both the input magnitudes and 
    colors. 
    Fig \ref{fig:psf_color} shows that \hscpipe{} provides precise and accurate PSF 
    colors for synthetic stars with realistic color distributions down to very 
    faint magnitudes. 
    The average precision for $(g-i)$ is ${\sim}0.025$ mag at 
    $i_{\mathrm{Input}}{\sim}19.0$. 
    The scatter increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}24.0$ mag.  
    The $(i-y)$ color displays similar precision. 
    The \forced{} PSF color measurements are not biased through the entire ranges of 
    input magnitudes and colors.

    Fig \ref{fig:psf_color} shows that the precision of PSF colors do not depend 
    the seeing conditions. 
    For instance, the precision of $(g-i)$ for the \texttt{badSeeing} \tract{} is 
    only slightly worse at the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the \texttt{goodSeeing} \tract{}.

@@

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} PSF Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.021 &   0.019 &   0.019 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.008 &   0.004 & \n0.004 & \n0.006 \\
    \hline 
    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.026 &   0.025 &   0.020 &   0.020 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.037 &   0.033 &   0.022 &   0.021 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.005 &   0.002 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.054 &   0.051 &   0.031 &   0.031 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.003 &   0.001 & \n0.001 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.077 &   0.075 &   0.058 &   0.057 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.002 & \n0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.105 &   0.105 &   0.109 &   0.123 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.009 & \n0.002 &   0.011 & \n0.002 \\
    \hline
    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.117 &   0.137 &   0.189 &   0.221 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.005 &   0.007 &   0.064 & \n0.063 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

>>>>

    In Fig \ref{fig:psf_color}, we evaluate the precision and accuracy of the 
    \forced{} $(g-i)$ and $(i-y)$ PSF colors by comparing the differences between input 
    and output colors ($\Delta \mathrm{Color}$) with both the input magnitudes and 
    colors. 
    Fig \ref{fig:psf_color} shows that \hscpipe{} provides precise and accurate PSF 
    colors for synthetic stars with realistic color distributions down to very 
    faint magnitudes. 
    The average precision for $(g-i)$ is ${\sim}0.023$ mag at 
    $i_{\mathrm{Input}}{\sim}19.0$. 
    The statistical scatter increases to ${\sim}0.16$ mag at 
    $i_{\mathrm{Input}}{\sim}25.0$ mag.  
    The $(i-y)$ color displays similar precision. 
    The \forced{} PSF color measurements are not biased through the entire ranges of 
    input magnitudes and colors.

    Fig \ref{fig:psf_color} shows that the precision of PSF colors do not depend 
    the seeing conditions. 
    For instance, the precision of $(g-i)$ for the \texttt{badSeeing} \tract{} is 
    only slightly worse at the very faint end (${\sim}0.18$ mag at
    $i_{\mathrm{Input}}{\sim}25.0$ mag) compared to the \texttt{goodSeeing} \tract{}.

@@

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} PSF Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.022 &   0.018 &   0.019 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline 
    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.028 &   0.024 &   0.019 &   0.019 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.034 &   0.031 &   0.022 &   0.022 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.006 &   0.002 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.053 &   0.051 &   0.031 &   0.030 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.004 &   0.001 & \n0.004 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.079 &   0.086 &   0.057 &   0.058 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.004 & \n0.015 & \n0.001 & \n0.004 \\
    \hline
    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.116 &   0.122 &   0.111 &   0.112 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.015 & \n0.001 &   0.009 &   0.004 \\
    \hline
    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.162 &   0.185 &   0.192 &   0.216 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.044 & \n0.018 &   0.097 &   0.097 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%
